Flow Data Organization

### 2017-03-01 Code_01 Data_Organization.Rmd

M.Data = left_join(Data.Preds, df, by = c("Station.ID","Date")) %>% 
	group_by(Station.ID, Year, nMonth, Month) %>% 
	summarise(median.M.flow = median(Flow.Data),
 						max.M.flow = max(mean5day, na.rm = T),
 						min.M.flow = min(mean5day, na.rm = T))
#Join location and area data to flow data.
M.Data = left_join(M.Data, WS.2, by = "Station.ID")
save(M.Data,file = "03_Data_Monthly.RData")
```

>>>>

M.Data = left_join(Data.Preds, df, by = c("Station.ID","Date")) %>% 
	mutate(flow.data_mean = if_else(is.na(.$mean5day), .$Flow.Data, .$mean5day)) %>%
	select(-mean5day) %>% 
	group_by(Station.ID, Year, nMonth, Month) %>% 
	summarise(median.M.flow = median(flow.data_mean),
 						max.M.flow = max(flow.data_mean, na.rm = T),
 						min.M.flow = min(flow.data_mean, na.rm = T))
#Join location and area data to flow data.
M.Data = left_join(M.Data, WS.2, by = "Station.ID")
save(M.Data,file = "03_Data_Monthly.RData")
```
